---
title: "Untitled"
output: html_document
---

install.packages("igraph")
install.packages("dplyr")
install.packages("ndtv")
install.packages("scatterplot3d")

```{r setup, include=FALSE}
library(igraph)
library(dplyr)
library ("ndtv")
library(scatterplot3d)
```

```{r}
setwd("/Users/priankas/Desktop/Colab_Project/Integ475Project/networks")

CC <- read.graph("net.graphml", format = "graphml")

clust <- clusters(CC)
CC <- induced.subgraph(CC, which(clust$membership == which.max(clust$csize)))
summary(CC)
```

This part rendered the date into a dynamic network. We first created a static network with 25 vertices. By creating active edges, we were able to convert this static network to a dynamic one. To test the network, we viewed it time 1. We also added labels onto the network. Afterwards, using render.d3movie code, we made this dynamic network into a network movie. 

We experimented with different illustrations of this dynamic network. Using filmstrip I was able to display the networks at different times all at once. Then, using the timePrism function, I graphed the dyanmic network with time on the y-axis. 
```{r}

CC <- network.initialize(10)

add.edges.active(CC,tail=1:9,head=c(2:9,1),onset=1:9, terminus=11)
add.edges.active(CC,tail=10,head=c(1:9),onset=10, terminus=12)

class(CC)

print(CC)

as.data.frame(CC)

CC

plot(CC)

plot(network.extract(CC,at=1))

elabels<-lapply(get.edge.activity(CC),
                function(spl){
                  paste("(",spl[,1],"-",spl[,2],")",sep='')
                })

plot(CC,displaylabels=TRUE,edge.label=elabels,
     edge.label.col='blue') 

render.d3movie(CC, displaylabels=TRUE)

filmstrip(CC,displaylabels=FALSE)

compute.animation(CC)

timePrism(CC,at=c(1,10,20),
          displaylabels=TRUE,planes = TRUE,
          label.cex=0.5)

timeline(CC)

```


```{r}
CC <- network.initialize(500)
msmAt50<-network.extract(CC,at=50)
network.size(msmAt50)
plot(msmAt50,coord=network.layout.animate.MDSJ(msmAt50),vertex.cex=0.5)
```